\Large \bf Dynamic Program Dialysis with Lya

### 2019-12-22 paper/draft.tex
Update intro

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Library Dialysis with Lya}

%for single author (just remove % characters)
\author{
{\rm Anonymous Author(s)}\\
\normalsize{Submission \#225, 12 pages}\\
\normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
% {\rm Grigoris Ntousakis}\\
% Technical University of Crete
% \and
% {\rm Nikos Vasilakis}\\
% Massachusetts Institute of Technology
}

@@

This paper introduces \emph{library dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
Such library over-reliance is a recent trend in software engineering:
  applications today rely recursively on hundreds of libraries, to the point where code written by their nominal developers is becoming only a small fraction of their total line count.
% On the surface, such reliance is beneficial, 
Despite its benefits, such over-reliance creates many challenges for developers, exactly because their little knowledge of and visibility in the internals of these libraries:
  for example, security auditing and performance profiling---already challenging in monolithic applications---become extremely difficult in the presence of deeply-nested third-party code.

To address these challenges, library dialysis is a general technique that allows extracting meaningful insights with only a few lines of analysis-specific code.
This feature is achieved by automating dynamic \fra, \ana, and \ass of applications at the level of individual modules and during program execution, by wrapping and transforming the underlying dependency graph.
Our dialysis prototype, \sys, targets the JavaScript ecosystem, which counts over 1M libraries and is used on the web, server, and mobile.
We use a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual modules as well as multi-module application programs---all with a surprisingly low developer effort and performance overhead:
  insightful analyses can be expressed in 10--20 lines of code, add a virtually imperceptible increase in the load latency of individual modules, and scale to real applications with hundreds of modules.

@@

Dynamic analysis is a type of program analysis performed by (and while) executing a program, with the goal of extracting information about the program and its execution.
Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics~\cite{analysis:10}.
Contrary to other types of analysis, its key benefits make it the primary (or only) candidate in a variety of scenarios---namely, ones that require:
  (i) current runtime information, such as profiling information, in view of changing workloads or use patterns~\cite{staticdynamic},
  (ii) accurate visibility into the execution, devoid of abstraction or approximation~\cite{staticdynamic},
  (iii) Turing-complete policies, where invariants themselves are arbitrary programs~\cite{contracts1, contracts2, contracts3},
  (iii) dynamic or runtime-reflection features~\cite{jsanalysis1, jsanalysis2}, such as the ones present in Python and JavaScript.

@@

Unfortunately, reaping these benefits comes with significant costs in terms of (often, both) developer effort and runtime performance.
Instrumenting the program often requires a good understanding of its internals.
Applying associated tools adds to this requirement, such as instrumentation framework, instruction sets, and other underlying primitives~\cite{pin, valgrind}.
Modifying the runtime environment of the program is also cumbersome, error-prone, and JavaScript's V8 engine.
Problem-specific solutions require significant investment outside the language's mental model---for example, performance tracing frameworks such as perf and dtrace each feature their own language for specifying tracing programs, different from the application's language.
---as a case in point, Jalangi reports XX overhed (exact overheads always depend on the specific analysis).

Both overheads are severely compounded by the use of third-party libraries, development-time constructs usually glued together without a full understanding of their internals.
Libraries are used pervasively nowadays to lower development costs and improve software quality, a recent phenomenon enabled by zero-cost of sharing:
% This over-reliance to third-party libraries is a recent phenomenon, 
  with the proliferation of language-specific package repositories, the effort of publishing and that of using a library have essentially dropped to zero.
As a result, applications today
  to the point that it is common for thousands of applications to depend on libraries that count only a few dozen lines:
  for example, leftpad and

This paper proposes a novel approach to dynamic analysis, termed \emph{module dialysis}\footnote{
  A method of deconstruction, often for the purposes of removing waste products or altering piecewise components.
  From ancient Greek diá ($\delta\iota\alpha$ ``inter-, through'') and lúein (``loosen''); synchronically, dia- + -lysis.
} and implemented in \sys.
Library dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual libraries. 
It operates during program execution, automating wrapping and transforming the underlying dependency graph, allowing developers to extract meaningful insights with only a few lines of analysis-specific code
By operating at the granularity of libraries, module dialysis has several benefits over full-fledged dynamic analysis:
  (i) it allows bolting library dialysis itself as a library onto existing runtime environments that do not feature dynamic analysis,
  (ii) it supports analysis expressions directly in the same language, tools, and abstractions as the host application language---eschewing low-level instrumentation, and
  (iii) it features significantly low runtime performance overheads, enabling the potential for toggling its use in production environments.

@@

To demonstrate the effectiveness of the proposed techniques, we build a prototype of library dialysis, called \sys, targeting the JavaScript ecosystem---featuring more than 1M libraries (cite), high code-reuse (cite), and a pressing need for usable dynamic analysis (cite).
We develop a diverse set of four analyses that infer practical information about the analyzed program---including an allow/deny security analysis, a profiling analysis showing hot modules, a synthesis-oriented analysis on input-output data, and an analysis enforcing a static union-based type system at runtime.
This set of analysis drives the design requirements for \sys and highlights the benefits of bolt-on module-aware dynamic analysis.
Finally, we we use \sys to evaluate these analyses on three different levels:
  (i) synthetic micro-benchmarks that highlight certain features and confirm the correctness of our analyses in a controlled environment;
  (ii) single-module meso-benchmarks that allow comparison with more traditional dynamic analysis frameworks; and
  (iii) end-to-end full-application macro-benchmarks that show behavior of the \sys system on realistic workloads.

\S\ref{bg}--\ref{eval} present our key contributions:
\begin{itemize}
\item \S\ref{bg} characterizes the shared needs of four case-study analyses for which no prior dynamic analysis framework meets their needs.
\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
\item \S\ref{impl} discuss our prototype implementation, \sys, as a pluggable library for the JavaScript ecosystem;
\item \S\ref{eval} implementation and evaluation of the four analyses, showing \sys can express insightful analyses in 10–20 lines of code, adds a virtually imperceptible increase in the load latency of individual modules, and scales to real applications with hundreds of modules.
\end{itemize}

>>>>

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Dynamic Program Dialysis with Lya}

%for single author (just remove % characters)
\author{
{\rm Anonymous Author(s)}\\
\normalsize{Submission \#225, 12 pages}\\
% \normalsize{Additional Anonymized Material: \href{https://git.io/JvfCf}{https://git.io/JvfCf}.}
% {\rm Grigoris Ntousakis}\\
% Technical University of Crete
% \and
% {\rm Nikos Vasilakis}\\
% Massachusetts Institute of Technology
}

@@

% Such library over-reliance is a recent trend: % in software engineering:
Applications today rely on hundreds of libraries, to the point where code written by their nominal developers is only a small fraction of their total line count.
% On the surface, such reliance is beneficial, 
Despite its benefits, this over-reliance creates many challenges, precisely due to the lack of knowledge of and visibility into library internals---for example, in the presence of deeply-nested third-party code, security auditing and performance profiling, already challenging in monolithic applications, become extremely difficult.

To address these challenges, we present \emph{program dialysis}, a novel dynamic-analysis technique specifically tailored to applications with many third-party libraries.
Combining name shadowing, context wrapping, and transformation of the underlying dependency graph, program dialysis automates dynamic \fra, \ana, and \ass of programs at the level of individual libraries during program execution.
% is a general technique that
It bolts onto existing languages, enabling analysis expressions in the source language, with only a few lines of analysis-specific code.
Our dialysis prototype, \sys, targets the JavaScript ecosystem counting over 1M libraries used on the web, server, and mobile.
We develop a series of case-studies to motivate \sys's design, and demonstrate how \sys allows the analysis of both individual libraries as well as multi-libraries application programs with low developer effort and performance overhead:
  insightful analyses can be expressed in 10--20 lines of code, add a virtually imperceptible increase in the load latency of individual libraries, and scale to real applications with hundreds of libraries.

@@

Dynamic analysis is a type of program analysis performed by (and while) executing a program, with the goal of extracting information about the program and its execution.
Such information may include the ability to infer execution invariants, check security constraints, and extract performance characteristics~\cite{analysis:10}.
Contrary to other types of analysis, its key benefits make it the primary (or only) candidate in a variety of scenarios---namely, ones that require:
  (i) current runtime information, such as profiling information, in view of changing load patterns~\cite{staticdynamic},
  (ii) accurate visibility into the execution, devoid of abstraction or approximation~\cite{staticdynamic},
  (iii) Turing-complete policies, where policies themselves are programs~\cite{contracts1, contracts2, contracts3},
  (iv) dynamic or runtime-reflection features, such as the ones present in Python and JavaScript~\cite{jsanalysis1, jsanalysis2}.

@@

Unfortunately, reaping these benefits comes with significant costs in terms of developer effort or runtime performance.
Manually instrumenting a program requires a good understanding of its internals. % instruction sets?
External tools such as instrumentation frameworks~\cite{pin, valgrind} and performance tracing tools~\cite{perf, dtrace} only add to the curve, as they feature their own language for specifying analyses. % usually different from the application's language.
Modifying the application's runtime environment such as the interpreter is cumbersome, error-prone, and requires development in a language that is different than that of the program.
Tools that virtualize execution~\cite{pin, valgrind, jalangi, roadrunner} have high performance costs---for example, Jalangi~\cite{jalangi} and RoadRunner~\cite{roadrunner} report No-Op analysis on the order of 26--32$\times$ and 52$\times$, respectively.
% Problem-specific solutions require significant investment outside the language's mental model---for example,  each ---as a case in point, Jalangi reports XX overhed (exact overheads always depend on the specific analysis).

Both effort and performance costs are severely compounded by the use of third-party libraries---development-time constructs usually glued together without a full understanding of their internals.
Their ubiquity is a recent phenomenon enabled by zero-cost code sharing~\cite{libs}
% Libraries are used pervasively today to lower development costs and improve software quality, 
% This over-reliance to third-party libraries is a recent phenomenon, 
  with the proliferation of language-specific package repositories, the effort of publishing and that of using a library are essentially zero.
As a result, applications frequently count hundreds of libraries, each often containing only a few lines of code~\cite{}. % how to say thousands of them depend on a 11-line lib?
Library-oriented analysis adds to the challenges of prior tools as
  (i) library boundaries disappear at runtime, and
  (ii) coarse-grained, high-level language semantics misalign with fine-grained, low-level instrumentation.

To address these challenges, we propose a novel approach to dynamic analysis, termed \emph{dialysis}\footnote{
  A method of deconstruction into elements often for the purposes of removing waste products or altering piecewise components.
  From ancient Greek diá ($\delta\iota\alpha$ ``inter-, through'') and lúein (``loosen''); synchronically, dia- + -lysis.
} and implemented in \sys.
Program dialysis is a general technique, applicable to any programming language, that enables dynamic fragmentation, analysis, and re-assembly of applications at the level of individual libraries. 
It operates during program execution, automating wrapping and transformation of the program's dependency graph, and allowing developers to extract meaningful insights with only a few lines of analysis-specific code
By operating at the granularity of libraries, dialysis has several benefits over prior work: %full-fledged dynamic analysis:
  (i) it allows bolting library dialysis itself as a library onto existing runtime environments with no dynamic analysis,
  (ii) it supports analysis expressions using the same language, tools, and abstractions as the host program language,
  (iii) it features significantly low runtime performance overheads, enabling the potential for toggling its use in production environments.

@@

To demonstrate its effectiveness, we evaluate \sys on the JavaScript ecosystem with over 1M libraries (cite), high code-reuse (cite), and a pressing need for usable dynamic analysis (cite).
We develop a diverse set of analyses that infer practical information about the analyzed program---including an allow/deny security analysis, a profiling analysis showing bottlenecked modules, a synthesis-oriented analysis on input-output data, and an analysis enforcing a static union-based type system at runtime.
This set of analysis drives the design requirements for \sys and highlights the benefits of our approach.
Finally, we use \sys to evaluate these analyses on three different levels:
  (i) synthetic micro-benchmarks that test certain aspects and confirm the correctness of our analyses in a controlled environment;
  (ii) single-module meso-benchmarks that allow comparison with dynamic analysis frameworks; and
  (iii) end-to-end full-application macro-benchmarks that show behavior of \sys on realistic workloads. 
\S\ref{bg}--\ref{eval} present our key contributions:
\begin{itemize}
\item \S\ref{bg} characterizes the shared needs of four case-study analyses for which no prior dynamic analysis framework meets their needs.
\item \S\ref{design} presents the design of the bolt-on module-oriented dynamic analysis~\sx{design}, which meets the requirements of the four case-study analyses.
\item \S\ref{impl} discusses our implementation, \sys, as a pluggable library for the JavaScript ecosystem, as well as the implementation of the four analyses.
\item \S\ref{eval} evaluates \sys showing it expresses insightful analyses succinctly, adds minimal overheads over the baseline runtime, and scales to hundreds of modules.
\end{itemize}
